Image Processing and geometrical analysis for profile detection during P-Gas Metal Arc Welding

### 2011-03-25 articles/MIG/paper-drop_v1.tex

\section{ The Analyzing methods}
\label{ the_analyze_methods}
Image treatment and implemented algorithms are dependent of the optical setup and recording of images.
Nevertheless even if shadowgraphy technic is modified, the algorithm to detect and measure profile during
welding will still be valid by modifying some parameters.

@@

\subsubsection{Edge extraction}
\label{edge_extraction}
\begin{description}
\item[ Macrodrop]

@@

\item[ Droplet]
To the droplet edge section, the white points cord defines 
the surface of the droplet. Note at figure \ref{fig::photo-droplet-canny} that the biggest closer
 cord correspond to the droplet section. The idea is to build segments around
 the cords, and take the longest closer segment.

@@

\end{description}

>>>>

\section{ Applying image processing}
\label{ applying_image_processing}
Image treatment and implemented algorithms are dependent of the optical setup and recording of images.
Nevertheless even if shadowgraphy technic is modified, the algorithm to detect and measure profile during
welding will still be valid by modifying some parameters.

@@

\subsection{Edge extraction}
\label{edge_extraction}

\subsubsection{Macrodrop}

@@

\subsubsection{Droplet}

To the droplet edge section, the white points cord defines 
the surface of the droplet. Note at figure \ref{fig::photo-droplet-canny} that the biggest closer
 cord correspond to the droplet section. The idea is to build segments around
 the cords, and take the longest closer segment.

@@
